\textbf{Designing a Virtual Security Management Layer for Cloud Content}

### 2016-02-03 tex/paper.tex
Added introduction to serving private content

\newpage
\section{Implementation}
\subsection{Background}
\subsubsection{The current system}
Today a system called battlebinary~\cite{BATTLEBINARY} is used for managing and uploading files,
mostly images, to content delivery networks. The current system does not make use out of the
security features that the CDN's are offering, instead it uses a form of security by obscurity. When
a file is uploaded to a CDN it is open for the public, but its filename is composed out of its
original filename concatenated with a part of the MD5 hash of the content of the file, which makes
it an extremely hard process to access the file on the CDN without access to the original file or a
reference to the URI.

@@

@@

\subsubsection{Security of the system}
\subsubsubsection{Authorization}
The authorization of users in the system is currently being handled by LDAP~\cite{LDAP}, as Perius 
is mainly focussed at being deployed in internal networks which usually has an LDAP service enabled. 
LDAP also makes it easier for the user to login as no separate account is needed for Perius and 
thus the user can use the same account as for all the LDAP connected services on the internal 
network.

\subsubsubsection{Audit logs}

\subsubsubsection{CDN Connections}
\fix Describe how the CDN connections are encrypted and secure.

When uploading files to the CDN networks their TLS/SSL protected API's are used to ensure that no
data leaks through packet sniffing etc. The files are grouped corresponding to their parent
containers in Perius, which makes it possible to handle the security settings for all files in a
group at once, without having to traverse through the tree in Perius.

\fix Describe the different CDN mechanisms, like signed cookies and urls

>>>>

\newpage
\section{Implementation}
\subsection{Background}
\subsubsection{The current system} \label{sec:current_system}
Today a system called battlebinary~\cite{BATTLEBINARY} is used for managing and uploading files,
mostly images, to content delivery networks. The current system does not make use out of the
security features that the CDN's are offering, instead it uses a form of security by obscurity. When
a file is uploaded to a CDN it is open for the public, but its filename is composed out of its
original filename concatenated with a part of the MD5 hash of the content of the file, which makes
it an extremely hard process to access the file on the CDN without access to the original file or a
reference to the URI.

@@

\subsection{Security of the system}
\subsubsection{Authorization}
The authorization of users in the system is currently being handled by LDAP~\cite{LDAP}, as Perius 
is mainly focussed at being deployed in internal networks which usually has an LDAP service enabled. 
LDAP also makes it easier for the user to login as no separate account is needed for Perius and 
thus the user can use the same account as for all the LDAP connected services on the internal 
network.

\subsubsection{Audit logs}

\subsubsection{CDN Connections}
\fix Describe how the CDN connections are encrypted and secure.

When uploading files to the CDN networks, their TLS/SSL protected API's are used to ensure that no
data leaks through packet sniffing etc. The files are grouped corresponding to their parent
containers in Perius, which makes it possible to handle the security settings for all files in a
group at once, without having to traverse through the tree in Perius.

\subsubsubsection{Serving private content}
\fix Describe the different CDN mechanisms, like signed cookies and urls

There are three different ways, that this implementation make use of, to make sure that 
the CDNs serve content in a private manner. The first two is signed URLs and signed cookies, and 
the third is a mixture between one of the first two together with a range of IP
addresses.~\cite{AWSPRIVATE} 
These mechanisms are needed, as explained in Section~\ref{sec:current_system}, to ensure that
assets are not leaked if an attacker manages to find out the URL for the asset.

\par \textbf{Signed URLs} \\
test test

\par \textbf{Signed cookies} \\
test test

\par \textbf{IP range restriction} \\
test test

@@
